Depression_Vis

### 2023-04-20 Depression_Vis.Rmd
Finalized code for final presentation.

```{r}
Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

@@

#### Race
```{r}
#Overall race
Mothership_Mean_CUDOS_Race<-Mothership_Long %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
   geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

@@

## GENDER IDENTITY
Create a New Data Set with an Average Depression Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 59, label = "Q1") +
  annotate("text", x = 8, y = 59, label = "Mean") +
  annotate("text", x = 13, y = 59, label = "Q3") 
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF1<-Mothership_Mean_CUDOS_Gender[1:30,]
# plot
Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
GenderDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 10-15 Days
GenderDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 16+ Days
GenderDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF4<-GenderDF4[1:120,]

@@

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Depression Variable and Track
Mothership_Mean_CUDOS_Track<-Mothership_Long %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUDOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

Break it up by duration group (Treatment track)
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
TrackDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
TrackDF1<-TrackDF1[1:20,]
# plot
Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by Track During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
TrackDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 10-15 Days
TrackDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 16+ Days
TrackDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
TrackDF4<-TrackDF4[1:80,]

@@

```{r}
ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Depression Variable and Education
Mothership_Mean_CUDOS_Ed<-Mothership_Long %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
EducationDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Education Level During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
EducationDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 10-15 Days
EducationDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 16+ Days
EducationDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
EducationDF4<-EducationDF4[1:180,]

@@

```{r}
ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
```
### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Depression Variable and Year
Mothership_Mean_CUDOS_Year<-Mothership_Long %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

str(Mothership_Long$TxYear)

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

>>>>

```{r}
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

@@

#### Race
```{r}
Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]

#Create a Time Variable
Mothership_Long_dep$TxDay <- NA
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10

#Overall race
Mothership_Mean_CUDOS_Race<-Mothership_Long_dep %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","darkgreen",
                              "#0098DB","#0065A3","#A0AFA1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
                              "lightgrey","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey","darkgreen",
                              "lightgrey","#0065A3","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

@@

## GENDER IDENTITY
Create a New Data Set with an Average Depression Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )
#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF1<-Mothership_Mean_CUDOS_Gender[1:30,]
# plot
Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
GenderDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 10-15 Days
GenderDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 16+ Days
GenderDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF4<-GenderDF4[1:120,]

@@

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Depression Variable and Track
Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUDOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group (Treatment track)
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
TrackDF1<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
TrackDF1<-TrackDF1[1:20,]
# plot
Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by Track During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
TrackDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 10-15 Days
TrackDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 16+ Days
TrackDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
TrackDF4<-TrackDF4[1:80,]

@@

```{r}
ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Depression Variable and Education
Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
                              "#0098DB","lightgrey","lightgrey",
                              "lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
EducationDF1<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Education Level During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
EducationDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 10-15 Days
EducationDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

##### 16+ Days
EducationDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
EducationDF4<-EducationDF4[1:180,]

@@

```{r}
ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
```
### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Depression Variable and Year
Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

str(Mothership_Long_dep$TxYear)

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#91A9F1","darkgreen",
                              "#0065A3","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey","lightgrey",
                              "lightgrey","lightgrey","lightgrey",
                              "#0065A3","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

```
```
